A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-08 body/appendix_roms.tex
appendix done, missing all stats and truck

In this Appendix,
we detail our generic method to generate the volumes $W$ used
in RB-RRT; with the example of HRP-2.

>>>>

In this Appendix,
we detail our method to generate the volumes $W$ used
in RB-RRT, with the example of HRP-2.

We consider the robot HRP-2, and proceed to the decomposition 
of its kinematic chain into four limbs $R^k$.
The arms are connected to the shoulders, and the legs to the root.
The obtained volumes $W$ are shown in Figure~\ref{fig:hrp2_w}.

\begin{figure}
\centering
  \begin{overpic}[width=1\linewidth]{figures/hrp2_w}
	\end{overpic}
\caption{The $W$ volumes computed for HRP-2. The red shapes are $W^0$. The green shapes represent the $W^k$.}
		   \label{fig:hrp2_w}
\end{figure}

\subsection{Step 1: computing the reachable workspace $W^k$ of a limb}

To generate a volume $W^k$, we proceed as follows:
\begin{enumerate}
\item Generate randomly $N$ valid limb configurations for $R^k$, for $N$ really large (say $100000$);
\item For each configuration, store the 3D position of the end effector joint relatively to the root of $R^k$; then compute the convex hull of the resulting point cloud;
\item The resulting polytope can contain a very large number of faces. A last step is thus to simplify it in a conservative way with the blender decimate tool (\url{http://wiki.blender.org/index.php/Doc:2.4/Manual/Modifiers/Generate/Decimate}). For HRP-2 we apply the operator with a ratio of $0.06$, resulting in a polytope of 38 faces for the arms and the legs.
\end{enumerate}

\begin{figure}
\centering
  \begin{overpic}[width=1\linewidth]{figures/roms}
	\end{overpic}
\caption{Different approximations of the range of motion of the right arm HRP-2. Left: non convex-hull, computed with the powercrust algorithm~\citep{Amenta:2001:PC:376957.376986}. Middle:
convex hull of the reachable workspace. Right: Simplified hull used in our experiments.}
		   \label{fig:hrp2_roms}
\end{figure}

Figure~\ref{fig:hrp2_roms} illustrate the obtained $W^k$ for HRP-2.
Regarding the procedure, we can see that step 2 is conservative (Figure~\ref{fig:hrp2_roms}--right), which 
is acceptable, especially because the lost set essentially relates to configurations close to singularity (they are close to the boundaries of the reachable workspace). We choose again to be less complete
but more efficient, regarding the number of collision tests to be performed by RB-RRT.
In step 1 on the other hand, selecting the convex hull (Figure~\ref{fig:hrp2_roms}--middle) instead of a minimum encompassing shape (Figure~\ref{fig:hrp2_roms}--left) may introduce false positives.
Concretely, because the false positive set intersects with $W^0$, the scaling volume of the robot torso, the induced error is compensated,
as verified by the date of Table~\ref{tab:requestpercent}.

\subsection{Step 2: computing the trunk scaling workspace $W^0$ of the robot}
To define the volume $W^0$ of HRP-2, we proceed in an empirical manner.
First, we compute the bounding boxes of the robot trunk, head, and upper legs (Figure~\ref{fig:hrp2_w} -- red shapes).
Then, we perform a scaling of these boxes by a factor $s$. For different values of $s$, we verify the true feasibility condition:
For a large number of configurati
ons that verify the reachability condition, we try to generate contact configurations. We plot 
the success rates obtained depending on $s$ (Figure~\ref{hrp2_w}). We then choose the minimal satisfying value of $s$.

### 2015-12-08 body/intro.tex
appendix done, missing all stats and truck

By tackling these issues, our method proposes contributions to both problems \Pa and \Pb.
For each problem, we introduce an original formulation of the related theoritical issues.
Then, we propose a concrete implementation of the solution, where the constraints of the problem are relaxed in favor of efficiency.
The relaxation is justified empirically, with statistics presented for each robot and scenario presented. The complete framework is implemented within
the open source platform Hpp.

@@

The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep(tonneauisrr15).
The conference paper focuses on the theoritical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with an argumented discussion on the implementation of this theory to real world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot. We also provide details on the hpp implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real robot models, namely HRP-2 and Hyq. TODO Appendix describes the generation process
for the robot.

>>>>

By tackling these issues, our method proposes contributions to both problems \Pa and \Pb.
For each problem, we introduce an original formulation of the related theoritical issues.
Then, we propose a concrete implementation of the solution, where the constraints of the problem are relaxed in favor of efficiency.
The relaxation is justified empirically, with statistics presented for each robot and scenario presented. The complete framework is implemented within
the open source platform HPP.

@@

The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep(tonneauisrr15).
The conference paper focuses on the theoritical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with an argumented discussion on the implementation of this theory to real world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot. We also provide details on the HPP implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real robot models, namely HRP-2 and Hyq. TODO Appendix describes the generation process
for the robot.
